Microxanox: an R package for simulating an aquatic $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states.

### 2023-09-06 inst/manuscript/manuscript_microxanox.Rmd
Draft Revision 2

As discussed in the Introduction section, the package was motivated by the question of how biodiversity influences ecosystem responses to environmental change. Extensive results concerning this question are given in a separate publication @Limberger2023. Here we describe one of the results, which is that having biodiversity in a functional group can allow state changes to occur that otherwise would not have, i.e. biodiversity can qualitatively change the state of the ecosystem.

>>>>

As discussed in the Introduction section, the package was motivated by the question of how biodiversity influences ecosystem responses to environmental change. Extensive results concerning this question are given in a separate publication @Limberger2023. Here describe one of the results, which is that having biodiversity in a functional group can allow state changes to occur that otherwise would not have, i.e. biodiversity can qualitatively change the state of the ecosystem.
